### 2017-10-13 Gruba/04-uc.tex

Providing the \textit{Feature Data}, User Clustering takes the charge of grouping each user concerned into a proper cluster.
Algorithm \ref{alg:uc} illustrates such overall procedure.
%
The idea is to enumerate a number of clustering trials (line \ref{enu}) and select the optimal solution with the best Silhouette coefficient value ($v$ in line \ref{opti}).
In principle, each trial (referred by $t$ in line \ref{enu}) first performs a clustering task (line \ref{task}; to be detailed in section \ref{sec:cluster}), resulting a cluster (by $l(u)$) for each user $u$ (line \ref{l});
then, each user obtains a Silhouette coefficient value $v(u)$ stemmed from the in/out-cluster distances (lines \ref{v-b}--\ref{v-e}; shall be illustrated in section \ref{sec:compu});
finally, the averaged Silhouette coefficient value of all users serves as the Silhouette coefficient value of the current trial, written as $v(t)$ (line \ref{avg}), by which the said selection process is conducted (line \ref{opti}).

\begin{algorithm}[t]
\begin{small}
\caption{User Clustering in \sys{}}
\label{alg:uc}

\begin{algorithmic}[1]
\State Input: \textit{Feature Data} of users $\{F(u)\}$, the minimum/maximum number of clusters $N_i$ and $N_a$
\State Output: Optimal user clustering result $R$
\\
\ForAll {$t \in [N_i, N_a]$} \label{enu}
	\State group users $\{u\}$ into $t$ clusters by $\{F(u)\}$ \label{task}
	\State clustering result $R'(t)\ =\ \{(u,\ l(u))\}$ with cluster info $l(u)$ for each user $u$ \label{l}
	\ForAll {$u \in \{u\}$}
		\State in-cluster distance $d_i(u)$ \label{v-b}
		\State out-cluster distance $d_o(u)$
		\State Silhouette coefficient value $v(u)\ =\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}$ \label{v-e}
	\EndFor
	\State $v(t)\ =\ Avg\{v(u)\}$ \label{avg}
\EndFor
\If {$v(a)\ ==\ \ Max\{v(t)\}$} \label{opti}
	\State $R$ = $R'(a)$
\EndIf
\State \bfseries{return} $R$
\end{algorithmic}
\end{small}
\end{algorithm}

>>>>

Providing the \textit{Feature Data}, the User Clustering module takes the charge of grouping each user concerned into a proper cluster,
as illustrated in  Algorithm \ref{alg:uc}.
%
The idea is to enumerate a number of clustering trials (line \ref{enu}) and select the optimal solution with the best Silhouette coefficient value ($v$ in line \ref{opti}).
In principle, each trial (referred by $t$ in line \ref{enu}) first performs a clustering task (line \ref{task}; to be detailed in section \ref{sec:cluster}), resulting a cluster (by $l(u)$) for each user $u$ (line \ref{l});
then, each user obtains a Silhouette coefficient value $v(u)$ stemmed from the in/out-cluster distances (lines \ref{v-b}--\ref{v-e}; shall be illustrated in section \ref{sec:compu});
finally, the averaged Silhouette coefficient value of all users serves as the Silhouette coefficient value of the current trial, written as $v(t)$ (line \ref{avg}), by which the said selection process is conducted (line \ref{opti}).

\begin{algorithm}[t]
\begin{small}
\caption{User Clustering in \sys{}}
\label{alg:uc}
\begin{algorithmic}[1]
\State Input: \textit{Feature Data} $F$  of a set of users, the minimum/maximum number of clusters $N_i$ and $N_a$
\State Output: Optimal user clustering result $R$
\vspace{1ex}
\ForAll {$t \in [N_i, N_a]$} \label{enu}
	\State group users into $t$ clusters by $F$; \label{task}
	\State clustering result $R'(t)\ =\ \{(u,\ l(u))\}$ with cluster info $l(u)$ for each user $u$; \label{l}
	\ForAll {$u \in \{u\}$}
		\State in-cluster distance $d_i(u)$ \label{v-b};
		\State out-cluster distance $d_o(u)$;
		\State Silhouette coefficient value $v(u)\ =\ \frac{(d_o - d_i)}{max(d_o,\ d_i)}$; \label{v-e}
	\EndFor
	\State $v(t)\ :=\ Avg\{v(u)\}$; \label{avg}
\EndFor
\If {$v(a)\ =\ \ Max\{v(t)\}$}; \label{opti}
	\State $R$ := $R'(a)$;
\EndIf
\State \bfseries{return} $R$.
\end{algorithmic}
\end{small}
\end{algorithm}
